Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/results-type.tex
finished data type section

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario. We present various statistical models in section \ref{sec:regression} to support this conclusion. The 10 most and 10 least concerning data types can be seen in Table \ref{top10-table}.

Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information. As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, and are almost unanimously considered to be concerning. Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.

Also regardless of the other factors, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken). As seen in Table \ref{top10-table}, participants had spread distributions in perceptions regarding such information.  A possibility is that people rated these as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.

{\color {red} talk about the variance of the data types here, referring to the table in the appendix. Which were the highest in variance? Which were the unanimous? Which one had a spread? Were there any that were specifically polarized? J has yet to give me the table for this so I can talk about it. But the most unanimous ones seemed to be the highest-concerning ones, whereas the least concerning ones were more distributed. There are not any which are unanimously considered medium risk or to be not risky.}

@@

The data types examined span several existing and future use cases. We do not believe they are comprehensive in coverage of how wearable devices might capture data nor for all possible future use cases of the data. Therefore, we coded each data type in two ways: firstly in terms in the data and how it was captured (e.g., video, audio, text, etc.), and  secondly in terms of the type of risks presented to the user. This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results. Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}

The data captured fell into the following six possible categories:

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information
\end{enumerate}

The associated risks data type fell into the following five categories:

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} The risk involves the loss of money or property.
\item {\bf Image:} The risk involves loss of control over one's self-image (e.g., publicizing something embarrassing).
\item {\bf Medical:} The risk involves disclosure of medical information.
\item {\bf Physical:} The risk involves physical harm to the user.
\item {\bf Relationships:} The risk involves damage to the user's inter-personal relationships.
\end{enumerate}

>>>>

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data being shared. We present various statistical models in section \ref{sec:regression} to support this conclusion. The 10 top and bottom concerning data can be seen in Table \ref{top10-table}, and the full list of data can be seen in Appendix [?].

Participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information. As seen in Table \ref{top10-table}, photos and videos accounted for 5 of the top 10 concerns, and are almost unanimously considered to be concerning. Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.

Participants were least concerned about data that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken) and information available to advertisers (e.g. TV shows watched, music on device). As seen in Table \ref{top10-table}, participants had spread distributions in perceptions regarding such information.  These may have appeared as unconcerning because of unfamiliarity in what applications would use this data for, or because there does not seem to be any immediate financial, social, or physical consequences from having this information shared.

For the complete ranked list of data considered in this study, see Appendix [?]. Although certain data is considered unanimously upsetting to have shared, it is interesting to note that no data was considered unanimously non-upsetting to have shared, nor any data which evoked strong disagreement on how upsetting it was. Generally,  the rank of the data being shared is negatively correlated with the standard deviation of the answers.

@@

The data types examined span several existing and future use cases. We do not believe they are comprehensive in coverage of how wearable devices might capture data nor for all possible future use cases of the data. Therefore, we coded each data type in two ways: firstly in terms in the data and how it was captured (e.g., video, audio, text, etc.), and  secondly in terms of the type of risks presented to the user. This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results. Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}.

The data fell into the following six possible categories:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information
\end{enumerate}

The associated risks fell into the following five categories:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} The risk involves the loss of money or property.
\item {\bf Image:} The risk involves loss of control over one's self-image (e.g., publicizing something embarrassing).
\item {\bf Medical:} The risk involves disclosure of medical information.
\item {\bf Physical:} The risk involves physical harm to the user.
\item {\bf Relationships:} The risk involves damage to the user's inter-personal relationships.
\end{enumerate}
